Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-07 supplement/06_bat_data.Rmd
correct figure
styler pass

```{r}
# read in roosts and select the Har Gershom roost
roosts = fread("data/Roosts.csv")
setnames(roosts, "Species", "roost_name")
roosts = roosts[roost_name == "Har Gershom"]

# define a simple distance function that is vectorised
get_distance_adhoc = function(x1, y1, x2, y2) {
  sqrt(((x2 - x1) ^2) + ((y2 - y1) ^2) )
}

# calculate distance to roost cave at Har Gershom
data_residence[, distance_roost := get_distance_adhoc(
  x1 = roosts$X, 
  x2 = data_residence$X, 
  y1 = roosts$Y, 
  y2 = data_residence$Y
)
]
```

@@

```{r}
# plot for sanity check --- this plot is not shown
fig_roost_exclude =
  ggplot(data_residence)+
  geom_point(
    aes(X, Y, col = distance_roost)
  )+
  geom_point(
    data = roosts,
    aes(X, Y),
    shape = 21, size = 4,
    fill = "blue",
    alpha = 0.5
  )+
  scale_colour_viridis_c(
    option = "B", direction = -1,
    trans = "log10",
    breaks = c(1000, 2500, 5000),
    labels = function(x) {
      scales::comma(
        x,
        scale = 0.001, suffix = "km"
      )
    },
    limits = c(1000, NA),
    na.value = "lightblue"
  )+
  ggspatial::annotation_scale(location = "br") +
  theme_test() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    legend.position = "top",
    legend.key.height = unit(2, "mm"),
    legend.title = element_text(vjust = 1)
  ) +
  coord_sf(
    crs = 2039
  )+
  labs(
    colour = "distance (km)"
  )
```

@@

```{r}
# filter for hour between 8pm and 5am and distance > 1km
data_residence <- atl_filter_covariates(
  data = data_residence,
  filters = c(
    "hour > 20 | hour < 5",
    "distance_roost > 1000")
)
```

@@

>>>>

```{r}
# read in roosts and select the Har Gershom roost
roosts <- fread("data/Roosts.csv")
setnames(roosts, "Species", "roost_name")
roosts <- roosts[roost_name == "Har Gershom"]

# define a simple distance function that is vectorised
get_distance_adhoc <- function(x1, y1, x2, y2) {
  sqrt(((x2 - x1)^2) + ((y2 - y1)^2))
}

# calculate distance to roost cave at Har Gershom
data_residence[, distance_roost := get_distance_adhoc(
  x1 = roosts$X,
  x2 = data_residence$X,
  y1 = roosts$Y,
  y2 = data_residence$Y
)]
```

@@

```{r}
# plot for sanity check --- this plot is not shown
fig_roost_exclude <-
  ggplot(data_residence) +
  geom_point(
    aes(X, Y, col = distance_roost)
  ) +
  geom_point(
    data = roosts,
    aes(X, Y),
    shape = 21, size = 4,
    fill = "blue",
    alpha = 0.5
  ) +
  scale_colour_viridis_c(
    option = "B", direction = -1,
    trans = "log10",
    breaks = c(1000, 2500, 5000),
    labels = function(x) {
      scales::comma(
        x,
        scale = 0.001, suffix = "km"
      )
    },
    limits = c(1000, NA),
    na.value = "lightblue"
  ) +
  ggspatial::annotation_scale(location = "br") +
  theme_test() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank(),
    legend.position = "top",
    legend.key.height = unit(2, "mm"),
    legend.title = element_text(vjust = 1)
  ) +
  coord_sf(
    crs = 2039
  ) +
  labs(
    colour = "distance (km)"
  )
```

@@

```{r}
# filter for hour between 8pm and 5am and distance > 1km
data_residence <- atl_filter_covariates(
  data = data_residence,
  filters = c(
    "hour > 20 | hour < 5",
    "distance_roost > 1000"
  )
)
```

@@

## Main text Figure 8

See Fig. 8 in the main text, made with QGIS.
